Compositional Quantitative Resource Analysis of C Programs

### 2014-06-26 paper/main.tex
more descriptions of the automatic analysis

>>>>

Another very technical rule is {\sc Q:Call}.  It needs to
account for the stack ``switching'' caused by the function
call, the argument/return value passing, and the preservation
of local variables.  We can sum up the requirements for
this rule as follows,
\begin{itemize}
\item
  any potential in the function pre/postcondition is equalized
  to its matching potential in the pre/precondition,
\item
  the potential of intervals $|\inter x y|$ is preserved
  if $x$ and $y$ are local variables,
\item
  and the unknown potentials after the call (e.g.
  $|\inter x g|$, with $x$ local and $g$ global)
  are zeroed out in the postcondition.
\end{itemize}
If $x$ and $y$ are local variables and $\code{f}(x,y)$ is
called, the rule takes care to split the potential of
$|\inter x y|$ in two parts, one part to perform the
computation in the function $f$ and one part to keep for
later use after the function call.  This splitting is
materialized in the equation $Q = P + S$.  Arguments in
the function precondition $(\Gamma_f, Q_f)$ are named
using a fixed vector $\Vargs$ of names different from
all program variables.  This prevents name conflicts
from happening and ensures that the substitution
$[\Vargs/\vec x]$ is meaningful.  Symmetrically,
we use the unique name $\Vret$ to represent the
return value in the function postcondition
$(\Gamma'_f, Q'_f)$.
